### 2024-08-22 chap_methodo/chap_methodo.tex
Including remarks from HJ (Rebuttals)

In EnergyScope Pathway, $\tau\textsubscript{\emph{phase}}$ aims at depreciating the value of expenses done in the future (see Equation (\ref{eq:path_annu_factor})). The discount rate accounted for in this annualisation factor, $i_{rate}$, is considered identical for all the technologies of the system. In line with \citet{limpens2021generating}, we set the nominal value to $i_{rate}=1.5\%$ which is lower than values taken in other studies, between 7.5\% and 12\% \cite{meinke2017energy,simoes2013jrc,EuropeanCommission2016}. Having a low-value discount rate favours less late expenses compared to a higher value of discount rate. In practice, the discount rate would vary depending on the technology investment risk. Depending on the technology readiness level, private investors would be more or less risk-averse. However, EnergyScope only considers the vision of a central planner where a single agent makes the investment decisions without differentiating the sources of the capital, \ie private and public. Assuming a differentiated discount rate would require making assumptions about the private-public distribution of the capital. For this reason, we have decided to keep an identical value of discount rate for all the technologies.

@@

\begin{figure}[htbp!]
\centering
\includegraphics[width=10cm]{MY_process_code.pdf}
\caption{Diagram of the iterative optimisation of the whole-energy system transition pathway. Myopic optimisation of the pathway consists of a sequence of smaller \gls{LP} problems limited to their respective 10-year time window. If the optimisation is not deterministic, step 3.3 is the one where the value of some parameters is changed due to uncertainties (see Section \ref{sec:meth:UQ}) or the actions taken by the Reinforcement Learning-agent (see Chapter \ref{chap:chap_RL})}
\label{fig:MY_process_code}
\end{figure}

@@

However, depending on the research questions to address, other pathway energy system models might be more appropriate given their better spatial resolution or higher techno-economical details, for instance. Such models can be used and combined with the other methodological tools presented in this chapter. Although, the main (and only) requirement is to keep a low computational time as getting relevant results from the following approaches usually requires $10^3\sim 10^4$ runs.  In our case, we have implemented the model to keep the time to run a pathway composed of 7 representative years below 15 minutes on a personal laptop.

@@

\subsection{Discussion and guidelines for future researchers}
\label{subsec:meth:UQ:discussion}
Carrying out a \acrfull{GSA} requires two steps: uncertainty characterisation and uncertainty quantification. Characterising the distribution followed by uncertain parameters requires a lot of data that are either seldom available or poorly documented in the literature. Consequently, once lower and upper bounds are computed following a method like the one developed by \citet{Moret2017}, a good practice is to consider uniform distribution. Preliminary analyses revealing key parameters impacting the most the feature of interest could direct further research to refine the characterisation of these parameters.

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.8\textwidth]{Schematics_RL.pdf}
\caption{The \Acrfull{RL} framework applied to the myopic optimisation of the energy transition pathway between 2020 and 2050. Here, the agent interacts with its environment, \ie the energy-system model on a limited decision window of 10 years. At the beginning of each episode, one different sample of uncertain parameters is drawn and affects the environment, EnergyScope Pathway, according to the methodology detailed in Section \ref{subsec:uncert_charac}.}
\label{fig:Schematics_RL}
\end{figure}

@@

Given the assumed absence of knowledge of the agent about the dynamics of the environment, \ie its transition or reward functions, we needed a so-called ``model-free'' learning algorithm. In practice, in a model-free approach, the agent estimates the optimal policy directly from experience and without estimating the dynamics of the environment. However, model-free methods suffer from two major drawbacks: their sample inefficiency and their sensitivity concerning their hyper-parameters (\eg learning rates, exploration constants) \cite{haarnoja2018soft}. The former leads to a too-expensive computational burden while the second requires meticulous settings to get good results.  To overcome these two challenges, we needed to choose between an ``on-policy'' or ``off-policy'' algorithm. In a nutshell, in on-policy learning, the agent learns the value function or policy based on the data it generates by following its current policy whereas, in off-policy, the agent can learn from data collected by any policy, not just the one it is currently following, which provides greater flexibility and potential for reusing data stored in the so-called replay buffer. This makes off-policy algorithms more data efficient and ensures better exploration by reusing past experiences or even following random exploration \cite{haarnoja2018soft}.

@@

Finally, we have assumed thresholds to limit the number of principal components of each representative year, $\text{PC}_y$ (90\%), the similarity between two of these $\text{PC}_y$ (90\%) and to limit the number of $\text{PC}_{text{transition}}$ (85\%). These thresholds have been defined based on good practices discussed in the literature and \textit{a posteriori} observations specific to our case study. We would recommend starting with these values and adapting them in a second time if needed to increase or decrease the level of detail captured by the PCs.

>>>>

In EnergyScope Pathway, $\tau\textsubscript{\emph{phase}}$ aims at depreciating the value of expenses done in the future (see Equation (\ref{eq:path_annu_factor})). The discount rate accounted for in this annualisation factor, $i_{rate}$, is considered identical for all the technologies of the system. In line with \citet{limpens2021generating}, we set the nominal value to $i_{rate}=1.5\%$ which is lower than values taken in other studies, between 7.5\% and 12\% \cite{meinke2017energy,simoes2013jrc,EuropeanCommission2016}. In the 30-year time window of the perfect foresight approach, having a higher value of discount rate would postpone investments in more capital-intensive assets. However, in a myopic vision, this effect is more limited given the shorter time window. In practice, the discount rate would vary depending on the technology investment risk. Depending on the technology readiness level, private investors would be more or less risk-averse. However, EnergyScope only considers the vision of a central planner where a single agent makes the investment decisions without differentiating the sources of the capital, \ie private and public. Assuming a differentiated discount rate would require making assumptions about the private-public distribution of the capital. For this reason, we have decided to keep an identical value of discount rate for all the technologies.

@@

\begin{figure}[htbp!]
\centering
\includegraphics[width=10cm]{MY_process_code.pdf}
\caption{Diagram of the iterative optimisation of the whole-energy system transition pathway. Myopic optimisation of the pathway consists of a sequence of smaller \gls{LP} problems limited to their respective 10-year time window. If the optimisation is not deterministic, step 3.3 is the one where the values of some parameters are changed due to uncertainties (see Section \ref{sec:meth:UQ}) or the actions taken by the Reinforcement Learning-agent (see Chapter \ref{chap:chap_RL})}
\label{fig:MY_process_code}
\end{figure}

@@

However, depending on the research questions to address, other pathway energy system models might be more appropriate given their better spatial resolution or higher techno-economical details, for instance. Such models can be used and combined with the other methodological tools presented in this chapter. Although, the main (and only) requirement is to keep a low computational time as getting relevant results from the following approaches usually requires $10^3\sim 10^4$ runs.  In our case, EnergyScope Pathway can run a pathway composed of 7 representative years below 15 minutes on a personal laptop.

@@

\subsection{Discussion and guidelines for future researchers}
\label{subsec:meth:UQ:discussion}
Carrying out a \acrfull{GSA} requires two steps: uncertainty characterisation and uncertainty quantification. Characterising the distribution followed by uncertain parameters requires a lot of data that are either seldom available or poorly documented in the literature. Consequently, once lower and upper bounds are computed following a method like the one developed by \citet{Moret2017}, a good practice is to consider uniform distributions. Preliminary analyses revealing key parameters impacting the most the feature of interest could direct further research to refine the characterisation of these parameters.

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.8\textwidth]{Schematics_RL.pdf}
\caption{The \Acrfull{RL} framework applied to the myopic optimisation of the energy transition pathway between 2020 and 2050. Here, the agent interacts with its environment, \ie the energy-system model on a limited decision window of 10 years. At the beginning of each episode, a different sample of uncertain parameters is drawn and affects the environment, EnergyScope Pathway, according to the methodology detailed in Section \ref{subsec:uncert_charac}.}
\label{fig:Schematics_RL}
\end{figure}

@@

Given the assumed absence of knowledge of the agent about the dynamics of the environment, \ie its transition or reward functions, we needed a so-called ``model-free'' learning algorithm. In Reinforcement Learning, the ``model'' stands for the dynamics ``action-state-reward'' between the environment and the agent. In practice, in a model-free approach, the agent estimates the optimal policy directly from experience and without estimating the dynamics of the environment. However, model-free methods suffer from two major drawbacks: their sample inefficiency and their sensitivity concerning their hyper-parameters (\eg learning rates, exploration constants) \cite{haarnoja2018soft}. The former leads to a too-expensive computational burden while the second requires meticulous settings to get good results.  To overcome these two challenges, we needed to choose between an ``on-policy'' or ``off-policy'' algorithm. In a nutshell, in on-policy learning, the agent learns the value function or policy based on the data it generates by following its current policy whereas, in off-policy, the agent can learn from data collected by any policy, not just the one it is currently following, which provides greater flexibility and potential for reusing data stored in the so-called replay buffer. This makes off-policy algorithms more data efficient and ensures better exploration by reusing past experiences or even following random exploration \cite{haarnoja2018soft}.

@@

Finally, we have assumed thresholds to limit the number of principal components of each representative year, $\text{PC}_y$ (90\%), the similarity between two of these $\text{PC}_y$ (90\%) and to limit the number of $\text{PC}_{\text{transition}}$ (85\%). These thresholds have been defined based on good practices discussed in the literature and \textit{a posteriori} observations specific to our case study. We would recommend starting with these values and adapting them in a second time if needed to increase or decrease the level of detail captured by the PCs.

### 2024-08-22 frontend/merci.tex
Including remarks from HJ (Rebuttals)

Thank you, thank you, far too kind

>>>>

C’est une bonne situation, ça, doctorant? Moi je ne crois pas qu’il y ait de bonne ou de mauvaise situation. Moi, si je devais résumer ma thèse aujourd’hui avec vous, je dirais que c’est d’abord des rencontres, des gens qui m’ont tendu la main, peut-être à un moment où je ne pouvais pas, où j’étais seul chez moi. Et c’est assez curieux de se dire que les hasards, les rencontres forgent un docteur… Parce que quand on a le goût de la chose, quand on a le goût de la chose bien faite, le beau geste, parfois on ne trouve pas l’interlocuteur en face, je dirais, le miroir qui vous aide à avancer. Alors ce n’est pas mon cas, comme je le disais là, puisque moi au contraire, j’ai pu ; et je dis merci aux personnes qui m'ont aidé dans cette aventure, je leur dis merci, je chante ces personnes, je danse ces personnes… Je ne suis que reconnaissance !

% Promoteurs
Bien qu'un seul nom figure en couverture de cet ouvrage, les pages qui suivent seraient tristement restées vierges sans tout un environnement humain propice à la réflexion scientifique et à mon épanouissement personnel. Merci avant tout à mes deux promoteurs de thèse, mes deux ``pères académiques'', Hervé Jeanmart et Francesco Contino. Merci de m'avoir fait confiance dès le premier jour, donner la liberté de mener à bien mes recherches en toute autonomie tout en veillant à me prêter vos oreilles attentives et me prodiguer vos conseils avisés lors de nos échanges. Merci pour le temps que vous avez consacré lors de nos réunions pour résoudre les casse-têtes de ma thèse ainsi que ceux posés sur la table de Francesco. Merci à Hervé pour son pragmatisme et sa spontanéité et à Francesco pour son empathie et son goût du détail pour toujours chercher le dernier carat, à la limite parfois de la diptérophilie.

% Membres de jury
Merci aux membres de mon jury et encore plus aux membres de mon comité d'accompagnement, Sylvain Quoilin et Stefano Moret, pour le temps qu'ils ont consacré à la lecture de mon manuscrit et surtout pour les remarques toujours bienveillantes et constructives adressées lors de nos réunions et de la défense privée. Celles-ci m'ont permis d'apporter des améliorations majeures au texte et de mettre en exergue de futures pistes de recherche.

% UCLouvain + BEST + Véro
Pour avoir rendu lucrative cette aventure humaine et intellectuelle, je tiens à remercier l'UCLouvain mais aussi le SPF Economie au travers du Fonds de transition énergétique et du projet BEST. J'en profite pour dire un énorme merci à la coordinatrice de ce projet, Véronique Dias. Outre mes deux pères académiques, tu auras été une vraie mère, toujours aux petits soins pour moi et les autres chercheurs et chercheuses. Merci pour ton temps et ton investissement afin de faire de ce projet une franche réussite.

% Collègues en commençant par Gauthier et Diederik
Merci ensuite à mes parrains, Gauthier et Diederik. Vous m'avez catapulté dans cette aventure et m'avez toujours accompagné pour explorer de nouveaux horizons. Merci à Marion et Ignace pour votre écolage dans l'univers du Reinforcement Learning. Enfin, outre les tontons (parfois) un peu (trop) grincheux, je ne saurais qu'assez remercier tous mes frères et soeurs/cousins et cousines de cette belle et grande famille du TFL. Dans le désordre, merci Alice pour ton humour et tes goûts musicaux ``discutables'' et avoir tenté tant bien que mal de m'initier à la science de la musique et à la culture flamande. Merci Arnaud pour ton amitié de longue date, ta disponibilité, tes relectures et tes opinions toujours magistralement construites. Merci coach PB de m'en avoir fait baver et de m'avoir poussé à dépasser mes limites lors de nos nombreuses courses. Merci Youyou d'y avoir supporté nos discussions de darons (et de me botter désormais les fesses). Merci Mamasita Aurel pour ta good vibe et ton eau pet', Martinos pour la co-création du label, Paolito pour ta force tranquille, Antoine aka Jabiru pour ton abonnement au MR magazine, p'tit Louis pour avoir toujours si bien veillé à ma roue arrière, Zakito pour ton grand coeur, Nicou pour ton flow et tes serrages. Merci Sara de ne pas me détester. Xie xie Yanan for the hot pot.

% Amis et famille
Je remercie aussi du fond du coeur ma famille, ma belle-famille et mes amis. Merci pour votre amour et votre indéfectible soutien qui m'ont permis d'avancer jusqu'ici et de devenir qui je suis.

% Chloé et les enfants
Last but not least, je remercie ma compagne, Chloé. Merci pour ton oreille attentive et bienveillante surtout dans mes moments d'errance quand j'envisageais une reconversion en tant que jardinier ou éleveur de chèvres en Suisse. Je te remercie aussi d'être celle qui m'accompagne au quotidien depuis toutes ces années, et, surtout, d'être la formidable maman de nos deux enfants, Victor et Oscar, et de me permettre ainsi d'exercer le plus beau métier du monde.

% Autres
Ci-dessus n'était que l'humble expression de ma profonde gratitude envers celleux qui m'ont accompagné tout au long de ce chemin tantôt long fleuve tranquille tantôt parcours semé d'embûches. J'ai certainement omis de mentionner nombreux d'entre vous. Sachez cependant que sans votre présence et votre soutien, ce beau projet professionnel mais, avant tout, cette fabuleuse aventure personnelle n'aurait pas été possible.

### 2024-08-22 options/symbols_and_cmd.tex
Including remarks from HJ (Rebuttals)

% ---------------------------------------------------------------------------- %
% ACRONYMS
%% A
\newabbreviation[group={Acronyms}]{API}{API}{Application Programming Interface}

%% B
\newabbreviation[group={Acronyms}]{BECCS}{BECCS}{Bioenergy with Carbon Capture and Storage}
\newabbreviation[group={Acronyms}]{BEMS}{BEMS}{Building Energy Management System}
\newabbreviation[group={Acronyms}]{BEV}{BEV}{Battery Electric Vehicles}
\newabbreviation[group={Acronyms}]{BTX}{BTX}{Benzene, Toluene and Xylene}

%% C
\newabbreviation[group={Acronyms}]{CAPEX}{CAPEX}{Capital Expenditure}
\newabbreviation[group={Acronyms}]{CCGT}{CCGT}{Combined Cycle Gas Turbine}
\newabbreviation[group={Acronyms}]{CCS}{CCS}{Carbon Capture and Storage}
\newabbreviation[group={Acronyms}]{CHP}{CHP}{Combined Heat and Power}
\newabbreviation[group={Acronyms}]{CNG}{CNG}{Compressed Natural Gas}

%% D
\newabbreviation[group={Acronyms}]{DC}{DC}{Direct Current}
\newabbreviation[group={Acronyms}]{DHN}{DHN}{District Heating Network}
\newabbreviation[group={Acronyms}]{DNN}{DNN}{Deep Neural Network}
\newabbreviation[group={Acronyms}]{DRL}{DRL}{Deep Reinforcement Learning}

%% E
\newabbreviation[group={Acronyms}]{ESOMs}{ESOMs}{Energy System Optimisation Models}
\newabbreviation[group={Acronyms}]{ESTD}{ESTD}{EnergyScope Typical Days}
\newabbreviation[group={Acronyms}]{EUD}{EUD}{End-Use Demand}

%% F
\newabbreviation[group={Acronyms}]{FC}{FC}{Fuel Cell}
\newabbreviation[group={Acronyms}]{FEC}{FEC}{Final Energy Consumed}

%% G
\newabbreviation[group={Acronyms}]{GDP}{GDP}{Gross Domestic Product}
\newabbreviation[group={Acronyms}]{GHG}{GHG}{Greenhouse Gases}
\newabbreviation[group={Acronyms}]{GSA}{GSA}{Global Sensitivity Analysis}
\newabbreviation[group={Acronyms}]{GWP}{GWP}{Global Warming Potential}

%% H
\newabbreviation[group={Acronyms}]{HP}{HP}{Heat Pump}
\newabbreviation[group={Acronyms}]{HT}{HT}{High-Temperature}
\newabbreviation[group={Acronyms}]{HVC}{HVC}{High-Value Chemicals}

%% I
\newabbreviation[group={Acronyms}]{IAMs}{IAMs}{Integrated Assessment Models}
\newabbreviation[group={Acronyms}]{ICE}{ICE}{Internal Combustion Engine}
\newabbreviation[group={Acronyms}]{IEA}{IEA}{International Energy Agency}
\newabbreviation[group={Acronyms}]{IPCC}{IPCC}{Intergovernmental Panel on Climate Change}
\newabbreviation[group={Acronyms}]{IQR}{IQR}{Interquatile Range}

%% L
\newabbreviation[group={Acronyms}]{LCA}{LCA}{Life Cycle Assessment}
\newabbreviation[group={Acronyms}]{LCOE}{LCOE}{Levelised Cost of Energy}
\newabbreviation[group={Acronyms}]{LFO}{LFO}{Light Fuel Oil}
\newabbreviation[group={Acronyms}]{LOO}{LOO}{Leave-One-Out}
\newabbreviation[group={Acronyms}]{LP}{LP}{Linear Programming}
\newabbreviation[group={Acronyms}]{LPG}{LPG}{Liquefied Petroleum Gas}
\newabbreviation[group={Acronyms}]{LT}{LT}{Low-Temperature}

%% M
\newabbreviation[group={Acronyms}]{MDP}{MDP}{Markov Decision Process}
\newabbreviation[group={Acronyms}]{MMSA}{MMSA}{Methanol Market Services Asia}
\newabbreviation[group={Acronyms}]{MTBE}{MTBE}{Methyl Tert-butyl Ether}
\newabbreviation[group={Acronyms}]{MTO}{MTO}{Methanol-to-olefins}

%% N
\newabbreviation[group={Acronyms}]{NED}{NED}{Non-energy Demand}
\newabbreviation[group={Acronyms}]{NG}{NG}{Fossil Gas}
\newabbreviation[group={Acronyms}]{NN}{NN}{Neural Network}
\newabbreviation[group={Acronyms}]{NRE}{NRE}{Non-renewable Energy}
\newabbreviation[group={Acronyms}]{NSC}{NSC}{Naphtha Steam Cracker}

%% O
\newabbreviation[group={Acronyms}]{OPEX}{OPEX}{Operational Expenditure}

%% P
\newabbreviation[group={Acronyms}]{PC}{PC}{Principal Component}
\newabbreviation[group={Acronyms}]{PCs}{PCs}{Principal Components}
\newabbreviation[group={Acronyms}]{PCA}{PCA}{Principal Component Analysis}
\newabbreviation[group={Acronyms}]{PCE}{PCE}{Polynomial Chaos Expansion}
\newabbreviation[group={Acronyms}]{PV}{PV}{Photovoltaic}

%% R
\newabbreviation[group={Acronyms}]{RE}{RE}{Renewable Energy}
\newabbreviation[group={Acronyms}]{RL}{RL}{Reinforcement Learning}

%% S
\newabbreviation[group={Acronyms}]{SAC}{SAC}{Soft Actor-Critic}
\newabbreviation[group={Acronyms}]{SMR}{SMR}{Small Modular Reactor}
\newabbreviation[group={Acronyms}]{SVD}{SVD}{Singular Value Decomposition}

%% S
\newabbreviation[group={Acronyms}]{TRL}{TRL}{Technology Readiness Level}

%% U
\newabbreviation[group={Acronyms}]{UQ}{UQ}{Uncertainty Quantification}

%% V
\newabbreviation[group={Acronyms}]{VRES}{VRES}{Variable Renewable Energy Sources}

@@

\renewcommand\glstreegroupheaderfmt[1]{\begingroup\textbf{#1}\vspace{-.2cm}\par\endgroup}
\glsfindwidesttoplevelname
\glsxtrsetgrouptitle{Acronyms}{Acronyms}
\glsxtrsetgrouptitle{rs}{Roman Symbols}
\glsxtrsetgrouptitle{gs}{Greek Symbols}
\glsxtrsetgrouptitle{ss}{Sub- Superscripts}
\glsxtrsetgrouptitle{o}{Operators}

>>>>

% ---------------------------------------------------------------------------- %
% ACRONYMS
%% A
\newabbreviation{API}{API}{Application Programming Interface}

%% B
\newabbreviation{BECCS}{BECCS}{Bioenergy with Carbon Capture and Storage}
\newabbreviation{BEMS}{BEMS}{Building Energy Management System}
\newabbreviation{BEV}{BEV}{Battery Electric Vehicles}
\newabbreviation{BTX}{BTX}{Benzene, Toluene and Xylene}

%% C
\newabbreviation{CAPEX}{CAPEX}{Capital Expenditure}
\newabbreviation{CCGT}{CCGT}{Combined Cycle Gas Turbine}
\newabbreviation{CCS}{CCS}{Carbon Capture and Storage}
\newabbreviation{CHP}{CHP}{Combined Heat and Power}
\newabbreviation{CNG}{CNG}{Compressed Natural Gas}

%% D
\newabbreviation{DC}{DC}{Direct Current}
\newabbreviation{DHN}{DHN}{District Heating Network}
\newabbreviation{DNN}{DNN}{Deep Neural Network}
\newabbreviation{DRL}{DRL}{Deep Reinforcement Learning}

%% E
\newabbreviation{ESOMs}{ESOMs}{Energy System Optimisation Models}
\newabbreviation{ESTD}{ESTD}{EnergyScope Typical Days}
\newabbreviation{EUD}{EUD}{End-Use Demand}

%% F
\newabbreviation{FC}{FC}{Fuel Cell}
\newabbreviation{FEC}{FEC}{Final Energy Consumed}

%% G
\newabbreviation{GDP}{GDP}{Gross Domestic Product}
\newabbreviation{GHG}{GHG}{Greenhouse Gases}
\newabbreviation{GSA}{GSA}{Global Sensitivity Analysis}
\newabbreviation{GWP}{GWP}{Global Warming Potential}

%% H
\newabbreviation{HP}{HP}{Heat Pump}
\newabbreviation{HT}{HT}{High-Temperature}
\newabbreviation{HVC}{HVC}{High-Value Chemicals}

%% I
\newabbreviation{IAMs}{IAMs}{Integrated Assessment Models}
\newabbreviation{ICE}{ICE}{Internal Combustion Engine}
\newabbreviation{IEA}{IEA}{International Energy Agency}
\newabbreviation{IPCC}{IPCC}{Intergovernmental Panel on Climate Change}
\newabbreviation{IQR}{IQR}{Interquatile Range}

%% L
\newabbreviation{LCA}{LCA}{Life Cycle Assessment}
\newabbreviation{LCOE}{LCOE}{Levelised Cost of Energy}
\newabbreviation{LFO}{LFO}{Light Fuel Oil}
\newabbreviation{LOO}{LOO}{Leave-One-Out}
\newabbreviation{LP}{LP}{Linear Programming}
\newabbreviation{LPG}{LPG}{Liquefied Petroleum Gas}
\newabbreviation{LT}{LT}{Low-Temperature}

%% M
\newabbreviation{MDP}{MDP}{Markov Decision Process}
\newabbreviation{MMSA}{MMSA}{Methanol Market Services Asia}
\newabbreviation{MTBE}{MTBE}{Methyl Tert-butyl Ether}
\newabbreviation{MTO}{MTO}{Methanol-to-olefins}

%% N
\newabbreviation{NED}{NED}{Non-energy Demand}
\newabbreviation{NG}{NG}{Fossil Gas}
\newabbreviation{NN}{NN}{Neural Network}
\newabbreviation{NRE}{NRE}{Non-renewable Energy}
\newabbreviation{NSC}{NSC}{Naphtha Steam Cracker}

%% O
\newabbreviation{OPEX}{OPEX}{Operational Expenditure}

%% P
\newabbreviation{PC}{PC}{Principal Component}
\newabbreviation{PCs}{PCs}{Principal Components}
\newabbreviation{PCA}{PCA}{Principal Component Analysis}
\newabbreviation{PCE}{PCE}{Polynomial Chaos Expansion}
\newabbreviation{PV}{PV}{Photovoltaic}

%% R
\newabbreviation{RE}{RE}{Renewable Energy}
\newabbreviation{RL}{RL}{Reinforcement Learning}

%% S
\newabbreviation{SAC}{SAC}{Soft Actor-Critic}
\newabbreviation{SMR}{SMR}{Small Modular Reactor}
\newabbreviation{SVD}{SVD}{Singular Value Decomposition}

%% S
\newabbreviation{TRL}{TRL}{Technology Readiness Level}

%% U
\newabbreviation{UQ}{UQ}{Uncertainty Quantification}

%% V
\newabbreviation{VRES}{VRES}{Variable Renewable Energy Sources}

@@

%\renewcommand\glstreegroupheaderfmt[1]{\begingroup\textbf{#1}\vspace{-.2cm}\par\endgroup}
\glsfindwidesttoplevelname
%\glsxtrsetgrouptitle{Acronyms}{Acronyms}
%\glsxtrsetgrouptitle{rs}{Roman Symbols}
%\glsxtrsetgrouptitle{gs}{Greek Symbols}
%\glsxtrsetgrouptitle{ss}{Sub- Superscripts}
%\glsxtrsetgrouptitle{o}{Operators}
